Results

### 2021-02-18 reports/results.Rmd
Updates results slightly

baseline_rbans(df_rbans) %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score") %>%
  filter(grepl("dim_", subtest), !is.na(session)) %>%
  ggplot(aes(subtest, score, fill = trenink)) +
    geom_boxplot() +
    geom_hline(yintercept = 0) +
    facet_wrap(~session) +
    theme(axis.text.x =  element_text(angle = 45, vjust = 1, hjust = 1)) +
    labs(y = "Baseline change", title = "Change in score vs the baseline split by the session")

>>>>

baseline_rbans(df_rbans) %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest",
                 values_to = "score") %>%
  filter(grepl("dim_", subtest), !is.na(session)) %>%
  ggplot(aes(subtest, score, fill = trenink)) +
    geom_boxplot() +
    geom_hline(yintercept = 0) +
    facet_wrap(~session) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
    labs(y = "Baseline change",
         title = "Change in score vs the baseline split by the session")
```
